Matrix Transposition and Symmetry: a case study on Superscalar Architectures\\

### 2024-11-26 latex/paper.tex
latex: mothodologie

>>>>

In this report we benchmark different implementations of matTranspose
and checkSymm, comparing implicit and explicit parallelism
techniques. In particular, the benchmarks will indicate changes in cache and SIMD performance,
speedup with multiple threads and compile flags optimizations. Data will be compared through tables
and visually via graphs such as the roofline model. All benchmarks
will be tested against every matrix sixe from $2^2$ to $2^{12}$
We will now explain the methodology for matTranspose.
The algorithms being benchmarked take a $N \times N$ square matrix and transpose it to another $N \times N$ output matrix.
The following will be benchmarked:
\begin{itemize}
\item matTranspose: naive implementation of matTranspose, iterating over rows and columns and
  swapping the items. (TODO: Code)
\item matTranspose columns: similar to matTranspose, but iterating first by columns and then by rows.
  The purpose of this implementation is to test different access patterns.
  swapping the items. (TODO: Code)
\item matTranspose half:
\item matTranspose cyclic:   old algorithms
\item matTranspose vectorization:
\item matTranspose unrolling outer:
\item matTranspose intrinsic:
\item matTranspose cyclic unrolled:
\item matTranspose intrinsic unrolled:
\item matTranspose omp:  all types
\item matTranspose ched: 3 types
\end{itemize}

We will now explain the methodology for checkSymm.
